Verifying Demonstrations

### 2018-02-14 paper/protocol.tex

\mode*
\section{Protocol}

@@

\begin{frame}
\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & cid\gets H(\text{manifesto}), \\
        & pid\gets PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\leftrightarrow P\colon & \text{perform distance bounding} \\
      W\colon & wid\gets PRF_{k_W}(pid), \\
        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & H(pid, wid, t_s, l, wsig) \\
      P\to S\colon & H(pid, wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig),\\
        & \SPK{k_W, \sigma_W}
          {wid = \PRF_{k_W}(pid), wsig = \PRF_{k_W}(wid, t_s, l), \sigma_W = 
            \Sign[k]{k_W}}{\top} \\
        %& NIZK(wid = PRF_{k_W}(pid), wsig = PRF_{k_W}(wid, t_s, l), \exists 
        %sign(k_W)) \\
      P\to S\colon & (pid, wid, t_s, l, wsig),\\
        & \SPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = 
          \Sign[k]{k_P}}{\top}
    \end{align*}
  \end{minipage}
  \mode<article>{%
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }}%
  \label{fig:ProtocolOverview}
\end{figure}
\end{frame}

>>>>

\mode*
\section{PRIVO: A protocol for protest outcome verification}

@@

\begin{frame}
\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & cid\gets H(\text{manifesto}), \\
        & pid\gets \PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\leftrightarrow P\colon &
        \DBPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = \Sign[k]{k_P}} \\
      W\colon & wid\gets \PRF_{k_W}(pid), \\
        & wsig\gets \PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & H(pid, wid, t_s, l, wsig) \\
      P\to S\colon & H(pid, wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig, \pi_W),\quad \text{where}\\
        & \pi_W = \SPK{k_W, \sigma_W}
          {wid = \PRF_{k_W}(pid), wsig = \PRF_{k_W}(wid, t_s, l), \sigma_W = 
            \Sign[k]{k_W}}{pid, wid, t_s, l, wsig} \\
        %& NIZK(wid = PRF_{k_W}(pid), wsig = PRF_{k_W}(wid, t_s, l), \exists 
        %sign(k_W)) \\
      P\to S\colon & (pid, wid, t_s, l, wsig, \pi_P),\quad \text{where}\\
        & \pi_P = \SPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = 
          \Sign[k]{k_P}}{pid, wid, t_s, l, wsig}
    \end{align*}
  \end{minipage}
  \mode<article>{%
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }}%
  \label{fig:ProtocolOverview}
\end{figure}
\end{frame}
